SciPy - some descriptive title here

### 2018-06-27 scipy-1.0/paper.tex

\textbf{Impact now}

>>>>

\textbf{Impact now}
SciPy has a strong developer community and a massive user base. GitHub
traffic metrics report roughly 20,000 unique visitors to the source
website between May 14 and May 27, 2018, with 721 unique copies (``clones")
of the code base over that roughly two-week period. The developer community
consists of 610 unique contributors of source code, with $>19,000$ commits
accepted into the code base (GitHub page data).

% need some better usage stats sources?
% SciPy stuff from njs blog: https://docs.google.com/spreadsheets/d/1lOLvSF0up4eZyv2ugZi-TM_GIs3gPCkGNIDKXS1Y3w4/edit#gid=406031940
From the user side, there have been at least 15 million downloads
of the SciPy manylinux wheels between the start of 2016 and May of 2018
(njs blog). The recommended manuscript for citing SciPy,
published online 17 years ago, has been cited $>3000$
times. Some of the most prominent citing articles include the IPython
publication, a heavily-cited Nature Biotechnology article, a dark
matter annihlitation study in the field of cosmology, and many of the
other major downstream software libraries in the Python scientific
computing stack.
